### 2018-07-23 README.Rmd
update readme, fix URLs that were broken

	<td style="text-align:left;"><a href="https://www.assembla.com/spaces/sis/wiki/Red_List_API?version=3">link</a></td>

@@

	<td style="text-align:left;"><a href="https://opentreeoflife.org">link</a></td>

>>>>

	<td style="text-align:left;"><a href="http://apiv3.iucnredlist.org/api/v3/docs">link</a></td>

@@

	<td style="text-align:left;"><a href="https://github.com/OpenTreeOfLife/germinator/wiki/Open-Tree-of-Life-Web-APIs">link</a></td>
